---
title: "Weather Data of NY City"
author: "Sasmira Shetty"
date: "January 28, 2018"
output: ioslides_presentation
runtime: shiny
---

##Data Analysis - Summary
  
  - Analysis was done on airquality data of New York City for Five Months
  - Based on radio button selection, the x-axis is plotted. By default "Wind" is selected : Plot is shown in next slide
  - It was observed that Ozone decreased with increase in Wind,
  - Ozone Increased with increase in Solar and Temp
  - Ozone was maximum at 168 when Wind was 3.4, Solar was 238 and Temp was 81 in the month of August

##Plot
```{r eruptions, echo=FALSE}
     radioButtons("rd",
                    label="Select variable for X-Axis:",
                    choices=list("Wind","Solar","Temp"),
                    selected="Wind")
      checkboxInput("showlm", "Show/Hide Linear Model ", value = FALSE)
      

renderPlot({
   
    dataY<-airquality$Ozone
    dataX <- switch(input$rd,
                    Wind = airquality$Wind,
                    Solar = airquality$Solar.R,
                    Temp = airquality$Temp
                   )
    
    xlab<-input$rd
    ylab<-"Ozone"
    color <- ifelse(airquality$Month == 5, 'red',
                    ifelse(airquality$Month == 6, 'blue', 
                           ifelse(airquality$Month==7,'black',
                                  ifelse(airquality$Month==8,'yellow','green'))))
  if(input$rd=="Wind"){
    model <- lm(Ozone ~ Wind, data = airquality)

  }
    
    if(input$rd=='Solar'){
      model <- lm(Ozone ~ Solar.R, data = airquality)
      
    }
    if(input$rd=='Temp'){
      model <- lm(Ozone ~ Temp, data = airquality)
      
    }
    
     
   if(input$showlm){
     plot(dataX, dataY, xlab = xlab, ylab = ylab,col=color,pch=19 )
     legend('topright', legend = c('May','June','July','August','Sep'), col = c('red','blue','black','yellow','green'), cex = 0.8, pch = 19) 
     abline(model, col = "red", lwd = 2)
        }
      else{plot(dataX, dataY, xlab = xlab, ylab = ylab,col=color,pch=19 )
        legend('topright', legend = c('May','June','July','August','Sep'), col = c('red','blue','black','yellow','green'), cex = 0.8, pch = 19) 
      }
         
  })
```

##
```{r echo=TRUE, eval=FALSE}
##Code
     radioButtons("rd",
                    label="Select variable for X-Axis:",
                    choices=list("Wind","Solar","Temp"),
                    selected="Wind")
      checkboxInput("showlm", "Show/Hide Linear Model ", value = FALSE)
    
renderPlot({
    dataY<-airquality$Ozone
    dataX <- switch(input$rd,
                    Wind = airquality$Wind,
                    Solar = airquality$Solar.R,
                    Temp = airquality$Temp)
    xlab<-input$rd
    ylab<-"Ozone"
    color <- ifelse(airquality$Month == 5, 'red',
                    ifelse(airquality$Month == 6, 'blue', 
                           ifelse(airquality$Month==7,'black',
                                  ifelse(airquality$Month==8,'yellow','green'))))
```

##
```{r echo=TRUE, eval=FALSE}
  if(input$rd=="Wind"){
    model <- lm(Ozone ~ Wind, data = airquality)  }
    if(input$rd=='Solar'){
      model <- lm(Ozone ~ Solar.R, data = airquality)}
    if(input$rd=='Temp'){
      model <- lm(Ozone ~ Temp, data = airquality)  }
    
   if(input$showlm){
     plot(dataX, dataY, xlab = xlab, ylab = ylab,col=color,pch=19 )
     legend('topright', legend = c('May','June','July','August','Sep'), col = c('red','blue','black','yellow','green'), cex = 0.8, pch = 19) 
     abline(model, col = "red", lwd = 2)
        }
      else{plot(dataX, dataY, xlab = xlab, ylab = ylab,col=color,pch=19 )
        legend('topright', legend = c('May','June','July','August','Sep'), col = c('red','blue','black','yellow','green'), cex = 0.8, pch = 19) 
      }  })
  ```
