---
title: "Ozone and weather in  New York City"
author: "Sasmira Shetty"
date: "January 28, 2018"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The plot shows Ozone and weather in New York City for five months.
Depending on selection from user, the x axis is plotted at runtime. You can select appropriate radio button for Wind or Solar or Temp(x-axis variable) to plot the data with Ozone(y-axis variable).

User also has the option to view Linear Model, there is a check box with label "Show/Hide Linear Model" , on selecting this checkbox, the linear model will be shown in the plot for selected variable against radio button and Ozone. Unchecking the box will hide the linear model.

The Legend shows the color defined for each month.



This R Markdown document is made interactive using Shiny. Below is the same view as shown in the shiny app. 

It shows the Input values
 
 -Radio Button with label " variable for X-Axis:" , You can select one of the variable to plot the x-axis. By Default "wind" is selected.
 
 -Check Box with label "Show/Hide Linear Model", Linear Model will be shown in the plot if this is checked
 
 It shows the output
 
  -Plot as per the selected Input values, the legend shows the color for Months





```{r eruptions, echo=FALSE}
     radioButtons("rd",
                    label="Select variable for X-Axis:",
                    choices=list("Wind","Solar","Temp"),
                    selected="Wind")
      checkboxInput("showlm", "Show/Hide Linear Model ", value = FALSE)
      

renderPlot({
   
    dataY<-airquality$Ozone
    dataX <- switch(input$rd,
                    Wind = airquality$Wind,
                    Solar = airquality$Solar.R,
                    Temp = airquality$Temp
                   )
    
    xlab<-input$rd
    ylab<-"Ozone"
    color <- ifelse(airquality$Month == 5, 'red',
                    ifelse(airquality$Month == 6, 'blue', 
                           ifelse(airquality$Month==7,'black',
                                  ifelse(airquality$Month==8,'yellow','green'))))
  if(input$rd=="Wind"){
    model <- lm(Ozone ~ Wind, data = airquality)

  }
    
    if(input$rd=='Solar'){
      model <- lm(Ozone ~ Solar.R, data = airquality)
      
    }
    if(input$rd=='Temp'){
      model <- lm(Ozone ~ Temp, data = airquality)
      
    }
    
     
   if(input$showlm){
     plot(dataX, dataY, xlab = xlab, ylab = ylab,col=color,pch=19 )
     legend('topright', legend = c('May','June','July','August','Sep'), col = c('red','blue','black','yellow','green'), cex = 0.8, pch = 19) 
     abline(model, col = "red", lwd = 2)
        }
      else{plot(dataX, dataY, xlab = xlab, ylab = ylab,col=color,pch=19 )
        legend('topright', legend = c('May','June','July','August','Sep'), col = c('red','blue','black','yellow','green'), cex = 0.8, pch = 19) 
      }
         
  })
  ```





